ggplot and the venn diagram for the lefse bars !

### 2020-12-20 scripts/44_ggplot_venn_lefse.Rmd
udpate

```{r}
res <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready_.cts.tsv.res$', full.names = T)

res_all <- res %>% 
  set_names(res) %>% 
  map_dfr(~ read_tsv(., col_names = c('feature','xx','direction','score','pval')) %>% 
        filter(!is.na(score)), .id = 'res') %>% 
  mutate(tbl = if_else(str_detect(res, 'pcts'), 'pathway', 'taxa')) %>% 
  mutate(res = str_replace(res, '^.+//',''),
         res = str_replace(res, '_lefse.+$',''))  %>% 
  rename(grp = res) %>% 
  mutate(grp = str_replace(grp, 'pull_','pull\\.')) %>% 
  separate(grp, into = c('cohort','outcome'), sep = '\\.')

@@

vars <- res_all %>% 
  distinct(outcome) %>% 
  pull(outcome)

@@

>>>>

## collect all of the res files

```{r}
res <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready_.+cts.tsv.res$', full.names = T)

res_all <- res %>% 
  set_names(res) %>% 
  map(~ read_tsv(., col_names = c('feature','xx','direction','score','pval')) %>% 
        filter(!is.na(score))) %>% 
  keep(~ nrow(.) > 0) %>% 
  bind_rows(.id = 'res') %>% 
  mutate(tbl = if_else(str_detect(res, 'pcts'), 'pathway', if_else(str_detect(res, 'kocts'), 'KO', 'taxa'))) %>% 
  mutate(res = str_replace(res, '^.+//',''),
         res = str_replace(res, '_lefse.+$',''))  %>% 
  rename(grp = res) %>% 
  mutate(grp = str_replace(grp, 'pull_','pull\\.')) %>% 
  separate(grp, into = c('cohort','outcome'), sep = '\\.')

@@

```

```{r}
vars <- res_all %>% 
  distinct(outcome) %>% 
  pull(outcome)

@@

```{r}
# for the KO table
library(KEGGREST)
res_all_list %>% pluck('KO') %>% 
  keep(str_detect(names(.), 'toxicity')) %>% 
  reduce(intersect) %>% 
  map(~ list(KOID = keggGet(.)[[1]]$ENTRY,
             KO_name = keggGet(.)[[1]]$NAME,
             KO_def = keggGet(.)[[1]]$DEFINITION),
             KO_pathway = keggGet(.)[[1]]$PATHWAY) %>%
  bind_rows()
```

## a PCOA to see how the data

```{r}
cts <- read_tsv('../data/shotgun_output/humann3/humann_final_out/pull_toxicity_kocts_cpm_unstratified.tsv') %>% 
  gather('sampleid', 'value', names(.)[2]:names(.)[ncol(.)]) %>% 
  rename(pathway =  names(.)[1]) %>% 
  spread('pathway', 'value') %>% 
  column_to_rownames('sampleid')
dist_bl <- vegan::vegdist(cts, method = 'bray')
bl_bc <- cmdscale(dist_bl, k = 2) 
pheno <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  mutate(sampleid = fid)
bl_bc %>% 
    as.data.frame() %>% 
    rownames_to_column('sampleid') %>% 
    inner_join(pheno, by = 'sampleid') %>% 
    ggpubr::ggscatter(x = 'V1', y = 'V2', color =  'center',  shape = 'toxicity') 
```
